### 2014-01-31 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Another tweak to the intro of DPP manuscript.

The software package \msb implements such an approach in an
approximate-Bayesian model-choice framework \citep{Hickerson2006,Huang2011}.
Given aligned sequence data for \npairs{} pairs of populations, \msb 
estimates the number of divergence events shared among the pairs, the timing of
the events, and the assignment of pairs to the events, while integrating out
uncertainty in demographic parameters and the genealogical history of the
sequences.
% samples over all the possible ways of assigning the divergences between the
% populations of each pair to 1--\npairs{} divergence events, while estimating
% the timing of the events and integrating out uncertainty in demographic
% parameters and the genealogical history of the sequences.
Thus, the method samples over all possible divergence models of differing
dimensionality (i.e., all the possible partitions of \npairs{} pairs to
1--\npairs{} divergence-time parameters), and, in so doing, estimates the
posterior probability of each model.

>>>>

The software package \msb implements such an approach in an
approximate-Bayesian model-choice framework \citep{Hickerson2006,Huang2011}.
Given aligned sequence data for \npairs{} pairs of populations, \msb 
estimates the number of divergence events shared among the pairs, the timing of
the events, and the assignment of pairs to the events, while integrating out
uncertainty in demographic parameters and the genealogical history of the
sequences.
% samples over all the possible ways of assigning the divergences between the
% populations of each pair to 1--\npairs{} divergence events, while estimating
% the timing of the events and integrating out uncertainty in demographic
% parameters and the genealogical history of the sequences.
Thus, the method samples over all possible divergence models of differing
dimensionality (i.e., all the possible partitions of \npairs{} pairs to
$1,2,\ldots,\npairs{}$ divergence-time parameters), and, in so doing, estimates
the posterior probability of each model.
